---
title: "Data_Import"
output: html_document
date: "2023-07-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(tidyverse)
library(dplyr)
```

Read in data
```{r}
#read in files
# data1 <- read_excel("~/Downloads/test1.xlsx") #, col_names = TRUE)
# data2 <- read_excel("~/Downloads/test2.xlsx", col_names = TRUE)
# Excel69420 <- read_excel("~/Downloads/69420Excel.xlsx", col_names = TRUE)

Output_df <- NA
Output_df

METRIC1 <- read_csv("~/Desktop/Coding/data/SSRT/metric1.csv")

## Rename df headers
head <- METRIC1[1,]
colnames(METRIC1) = head
data <- METRIC1[-1,]
View(data)
```

```{r}
# path="/Users/hannahwild/Desktop/OneDrive/Research/Thesis/ThesisProposal/Data/Results/sequences"
# files=dir(path,recursive=TRUE,pattern="txt")
# curtbl=matrix(nrow=length(files),ncol=5)
# for (i in c(1:length(files))){
# df=unlist(read.delim(paste0(path,"/",files[i]), header=FALSE, sep = ',') ) 


### start with the for loop to loop all of the participants within the file
```

## Overarching For loop
```{r}
Output_df <- NA
ds_sst <- NA

fn_score <- function(ds) { 
  # Mean SSD
  mean_ssd <- mean(ds[ds$condition == 1, ]$ssd)
  # Proportion of failed nogos
  p_failed_nogo <- 1 - mean(ds[ds$condition == 1, ]$response)
  # Go RTs
  go_rts <- ds[
    ds$condition == 0 &
      ds$rt > 0,
    ]$rt
  # n-th percentile of Go RTs
  rt_quantile <- quantile(go_rts, p_failed_nogo, names = FALSE)
  # SSRTi
  return(rt_quantile - mean_ssd)
}

#1. specify folder with files
  files <- list.files(path="~/Desktop/Coding/data/SSRT", pattern="*.csv")
  path  = "~/Desktop/Coding/data/SSRT"
#2. write a for loop to do the things for the length of files in your folder
  for (i in c(1:length(files))){
#3. Read in each file as the data
  data=read.csv(paste0(path,"/",files[i]))
  
## Prepping DF for analyses
#1. Correct the column headers 
  head <- data[1,]
  colnames(data) = head
  data <- data[-1,]
#2. select and create the new variables we need and put those into a new df 
  df <- data %>%
    select(
             #overall stuff
             Subject, Group, Block, SessionDate, SessionStartDateTimeUtc,GoCorrect:InitGoRT,
             PercentStop,PracticeBlock:StopCorr,Trial,BkGd,GoDur,
             #distress/ upset sliders
             NegDistress.Slider1.Value,NegUpset.Slider1.Value,NeuDistress.Slider1.Value,NeuUpset.Slider1.Value,
             PosDistress.Slider1.Value,PosUpset.Slider1.Value, 
             #RTstuff
             CorrectAnswer, EmotionalPic,Go.ACC,Go.DurationError,Go.OnsetTime,Go.RT, Go1s.ACC,
             #trauma 1 stuff
             Trauma1CogAvoi1.Slider1.Value,Trauma1Deperson1.Slider1.Value,Trauma1Derealiz.Slider1.Value,
             Trauma1Dissoc.Slider1.Value, Trauma1CogAvoi1.Slider1.Value,
             Trauma1Distress1.Slider1.Value,Trauma1EmotAvoi.Slider1.Value
             ) %>%
             # Change these varaibles to numbers instead of characters
    mutate(
             Subject = as.double(Subject),
             Group = as.factor(Group),
             Block =as.factor(Block),
             `Running[Block]` = as.factor(`Running[Block]`),
             Trial = factor(Trial),
             BkGd = as.factor(BkGd),
             Go_Stop_Trial = ifelse(BkGd == "Black", "Go",
                             ifelse(BkGd == "Red", "Stop", NA
                                    )),
            GoDur = as.double(GoDur),
            Go.ACC = as.double(Go.ACC),
            Go1s.ACC = as.double(Go1s.ACC),
            Go.RT = as.double(Go.RT),
            NegDistress = as.double(NegDistress.Slider1.Value),
            NegUpset = as.double(NegUpset.Slider1.Value),
            NeuDistress = as.double(NeuDistress.Slider1.Value),
            NeuUpset = as.double(NeuUpset.Slider1.Value),
            PosDistress = as.double(PosDistress.Slider1.Value),
            PosUpset = as.double(PosUpset.Slider1.Value),
            CogAvoi = as.double(Trauma1CogAvoi1.Slider1.Value),
            Deperson = as.double(Trauma1Deperson1.Slider1.Value),
            Derealiz = as.double(Trauma1Derealiz.Slider1.Value),
            Dissoc = as.double(Trauma1Dissoc.Slider1.Value), 
            CogAvoi = as.double(Trauma1CogAvoi1.Slider1.Value),
            Trauma_Distress = as.double(Trauma1Distress1.Slider1.Value),
            Emot_Avoid = as.double(Trauma1EmotAvoi.Slider1.Value)
            )
#3. Create new df used for SSRT analyses / wide data
  ssrt_df <- df %>%
      mutate(
        participant = Subject,
        block = `Running[Block]`,
        block = ifelse(`Running[Block]` == "PracticeBlock", 0,
                ifelse(`Running[Block]` == "Block1", 1,
                ifelse(`Running[Block]` == "Block2", 2,
                ifelse(`Running[Block]` == "Block3", 3,
                ifelse(`Running[Block]` == "EmotionTask", 4, NA
                       ))))),
        ssd = ifelse(is.na(GoDur), 0, GoDur),
        condition = ifelse(Go_Stop_Trial == "Go", 0,
                    ifelse(Go_Stop_Trial == "Stop", 1,NA
                           )),
        response = ifelse(Go.ACC == 1 | Go1s.ACC == 1, 1, 0),
        response = ifelse(is.na(response), 0, 1
                                    ),
        trial = Trial,
        rt = 
          ifelse(
          is.na(Go.RT), 0, Go.RT),
        block = as.integer(block),
        trial = as.integer(trial),
        ssd = as.integer(ssd),
        condition = as.integer(condition),
        response = as.integer(response),
        rt = as.integer(rt),
        participant = as.integer(participant)
            ) |>
    filter(
      !is.na(Trial)
    )

#4. Assign values of each block to their own df
    block1 <- ssrt_df  %>%
      filter(`Running[Block]` == "Block1")
    block2 <- ssrt_df  %>%
      filter(`Running[Block]` == "Block2")
    block3 <- ssrt_df  %>%
      filter(`Running[Block]` == "Block3")
    combined <- ssrt_df  %>%
      filter(`Running[Block]` == "Block2" | `Running[Block]` == "Block3")
    Emotion <- ssrt_df  %>%
      filter(`Running[Block]` == "EmotionTask")


## Prepping data for SSRT stuff
    
    FIGURE OUT WHAT IS GOING ON
#1. Create a new df that is in the specific order for the SSRT function
SSRT_DF <- block1 |>
  select(
    'block', 'trial', 'ssd', 'condition', 'response','rt','participant'
  ) |>
  filter(
    !is.na(condition)
  )


View(SSRT_DF)

ds_sst <- rbind(ds_sst, SSRT_DF)

## Pull out the information for the wide
#1. Participant number
participant <- df[1,1]

#2. Block 1 ---------------
# Mean Block 1 GoRT
B1_Mean_GoRT = mean(block1$Go.RT, na.rm = TRUE)
# Block 1 Go Trials Correct
B1_Go_ACC = sum(block1$Go.ACC, na.rm = TRUE)
# Block 1 Stop Trials correct
B1_Stop_ACC = sum(block1$Go1s.ACC, na.rm = TRUE)
# Block 1 SSRT
B1_SSRT = fn_score(subset(ds_sst_1))

#3. Block 2 ---------------
# Mean Block 2 GoRT
B2_Mean_GoRT = mean(block2$Go.RT, na.rm = TRUE)
# Block 2 Go Trials Correct
B2_Go_ACC = sum(block2$Go.ACC, na.rm = TRUE)
# Block 2 Stop Trials correct
B2_Stop_ACC = sum(block2$Go1s.ACC, na.rm = TRUE)
# Block 2 SSRT
B2_SSRT = fn_score(subset(ds_sst_2))

#4. Block 3 -----------------
# Mean Block 3 GoRT
B3_Mean_GoRT = mean(block3$Go.RT, na.rm = TRUE)
# Block 3 Go Trials Correct
B3_Go_ACC = sum(block3$Go.ACC, na.rm = TRUE)
# Block 3 Stop Trials correct
B3_Stop_ACC = sum(block3$Go1s.ACC, na.rm = TRUE)
# Block 3 SSRT
B3_SSRT = fn_score(subset(ds_sst_3))

#5. Combined Stuff ----------------
# Combined Mean Block 2 + Block 3 GoRT
Combined_Mean_GoRT = mean(combined$Go.RT, na.rm = TRUE)
# Combined Block 2 + Block 3 Go Trials Correct
Combined_Go_ACC = sum(combined$Go.ACC, na.rm = TRUE)
# Combined Block 2 + Block 3 Stop trials correct
Combined_Stop_ACC = sum(combined$Go1s.ACC, na.rm = TRUE)
# Combined Block 2 + Block 3 SSRT
Combined_SSRT = fn_score(subset(ds_sst_com))

#6. Slider stuff ------------------
# Slider Value for RSDI on each image type
# Trial 1
NegDistress     = Emotion$NegDistress[!is.na(Emotion$NegDistress)]
NegUpset        = Emotion$NegUpset[!is.na(Emotion$NegUpset)]

# Trial 2
NeuDistress     = Emotion$NeuDistress[!is.na(Emotion$NeuDistress)]
NeuUpset        = Emotion$NeuUpset[!is.na(Emotion$NeuUpset)]

# Trial 3
PosDistress     = Emotion$PosDistress[!is.na(Emotion$PosDistress)]
PosUpset        = Emotion$PosUpset[!is.na(Emotion$PosUpset)]

#Trial 4
Derealiz        = Emotion$Derealiz[!is.na(Emotion$Derealiz)]
Dissoc          = Emotion$Dissoc[!is.na(Emotion$Dissoc)]
Emot_Avoid      = Emotion$Emot_Avoid[!is.na(Emotion$Emot_Avoid)]

# Trial 5
CogAvoi         = Emotion$CogAvoi[!is.na(Emotion$CogAvoi)]
Deperson        = Emotion$Deperson[!is.na(Emotion$Deperson)] 
CogAvoi         = Emotion$CogAvoi[!is.na(Emotion$CogAvoi)]
Trauma_Distress = Emotion$Trauma_Distress[!is.na(Emotion$Trauma_Distress)]

## combine into one data frame (row)

output_data = data.frame(
    participant, 
    B1_Mean_GoRT, B1_Go_ACC, B1_Stop_ACC,B1_SSRT,
    B2_Mean_GoRT, B2_Go_ACC, B2_Stop_ACC,B2_SSRT,
    B3_Mean_GoRT, B3_Go_ACC, B3_Stop_ACC,B3_SSRT,
    Combined_Mean_GoRT, Combined_Go_ACC, Combined_Stop_ACC,Combined_SSRT,
    NegDistress, NegUpset, NeuDistress,NeuUpset, PosDistress, PosUpset, CogAvoi, Deperson, Derealiz, Dissoc, CogAvoi, 
    Trauma_Distress, Emot_Avoid 
)

# Add this persons stuff to the overall data frame output_df
    Output_df <- rbind(Output_df,output_data)
    Output_df
  }
  
    #delete the row of NAs
    Output_df <- Output_df[-1]
  Output_df
  
  ##### SSRT STUFf
  
  
  
  FIGURE OUT WTF IS GOING ON
  # Block 1
ds_sst_1 <- SSRT_DF 

#|>
  filter(block == 1)

# Block 2
ds_sst_2 <- ds_sst |>
  filter(block == 2)

# Block 3
ds_sst_3 <- ds_sst |>
  filter(block == 3)

# Combined
ds_sst_com <- ds_sst |>
  filter(block == 2 | block == 3)

View(ds_sst_1)

## Scoring the SRT 
# This is the SSRT function

## Scoring a participant 
fn_score(subset(ds_sst_1, participant = 1))
  
#now that the loop is done, write 
#write.csv(Output_df, "~/Desktop/Coding/data/SSRT_Output/Output.csv")
```

```{r}
# ## Rename df headers
# head <- data1[1,]
# colnames(data1) = head
# data1 <- data1[-1,]
# 
# 
# View(data1)
# 
# df <- data1 %>%
#   select(
#              #overall stuff
#              Subject, Group, Block, SessionDate, SessionStartDateTimeUtc,GoCorrect:InitGoRT, PercentStop,PracticeBlock:StopCorr,Trial,BkGd,GoDur,
#              #distress/ upset sliders
#              NegDistress.Slider1.Value,NegUpset.Slider1.Value,NeuDistress.Slider1.Value,NeuUpset.Slider1.Value, PosDistress.Slider1.Value,PosUpset.Slider1.Value, 
#              #other 
#              CorrectAnswer, EmotionalPic,Go.ACC,Go.DurationError,Go.OnsetTime,Go.RT, Go1s.ACC,
#              #trauma 1 stuff
#              Trauma1CogAvoi1.Slider1.Value,Trauma1Deperson1.Slider1.Value,Trauma1Derealiz.Slider1.Value,
#              Trauma1Dissoc.Slider1.Value, Trauma1CogAvoi1.Slider1.Value,
#              Trauma1Distress1.Slider1.Value,Trauma1EmotAvoi.Slider1.Value
#              ) %>%
#              mutate(
#                Subject = as.double(Subject),
#                Group = as.factor(Group),
#                Block =as.factor(Block),
#                `Running[Block]` = as.factor(`Running[Block]`),
#                Trial = factor(Trial),
#                BkGd = as.factor(BkGd),
#                Go_Stop_Trial = ifelse(BkGd == "Black", "Go",
#                                     ifelse(BkGd == "Red", "Stop", NA)
#                                       ),
#                GoDur = as.double(GoDur),
#                #CorrectAnswer = as.double(CorrectAnswer),
#                Go.ACC = as.double(Go.ACC),
#                Go1s.ACC = as.double(Go1s.ACC),
#                Go.RT = as.double(Go.RT),
#                NegDistress = as.double(NegDistress.Slider1.Value),
#                NegUpset = as.double(NegUpset.Slider1.Value),
#                NeuDistress = as.double(NeuDistress.Slider1.Value),
#                NeuUpset = as.double(NeuUpset.Slider1.Value),
#                PosDistress = as.double(PosDistress.Slider1.Value),
#                PosUpset = as.double(PosUpset.Slider1.Value),
#                CogAvoi = as.double(Trauma1CogAvoi1.Slider1.Value),
#                Deperson = as.double(Trauma1Deperson1.Slider1.Value),
#                Derealiz = as.double(Trauma1Derealiz.Slider1.Value),
#                Dissoc = as.double(Trauma1Dissoc.Slider1.Value), 
#                CogAvoi = as.double(Trauma1CogAvoi1.Slider1.Value),
#                Trauma_Distress = as.double(Trauma1Distress1.Slider1.Value),
#                Emot_Avoid = as.double(Trauma1EmotAvoi.Slider1.Value)
#                )
#                
# view(df)
# ssrt_df <- df %>%
#   mutate(
#     participant = Subject,
#     block = `Running[Block]`,
#     block = ifelse(`Running[Block]` == "PracticeBlock", 0,
#             ifelse(`Running[Block]` == "Block1", 1,
#             ifelse(`Running[Block]` == "Block2", 2,
#             ifelse(`Running[Block]` == "Block3", 3,
#             ifelse(`Running[Block]` == "EmotionTask", 4, NA
#                    ))))),
#     ssd = ifelse(is.na(GoDur), 0, GoDur),
#     condition = ifelse(Go_Stop_Trial == "Go", 0,
#                 ifelse(Go_Stop_Trial == "Stop", 1,NA
#                        )),
#     response = ifelse(Go.ACC == 1 | Go1s.ACC == 1, 1, 0),
#     response = ifelse(is.na(response), 0, 1
#                                 ),
#     trial = Trial,
#     rt = 
#       ifelse(
#       is.na(Go.RT), 0, Go.RT),
#     block = as.integer(block),
#     trial = as.integer(trial),
#     ssd = as.integer(ssd),
#     condition = as.integer(condition),
#     response = as.integer(response),
#     rt = as.integer(rt),
#     participant = as.integer(participant)
#         ) 
# 
# 
# summary(df$`Running[Block]`)
# 
# block1 <- ssrt_df  %>%
#   filter(`Running[Block]` == "Block1")
# block2 <- ssrt_df  %>%
#   filter(`Running[Block]` == "Block2")
# block3 <- ssrt_df  %>%
#   filter(`Running[Block]` == "Block3")
# combined <- ssrt_df  %>%
#   filter(`Running[Block]` == "Block2" & `Running[Block]` == "Block3")
# Emotion <- ssrt_df  %>%
#   filter(`Running[Block]` == "EmotionTask")
# 
# write_csv(data1, "~/Downloads/data1.csv")
```

## Prepping data for SSRT stuff
```{r}
# ds_sst <- ssrt_df |>
#   select(
#     'block', 'trial', 'ssd', 'condition', 'response','rt','participant'
#   ) |>
#   filter(!is.na(trial))
# 
# # Block 1
# ds_sst_1 <- ds_sst |>
#   filter(block == 1)
# 
# # Block 2
# ds_sst_2 <- ds_sst |>
#   filter(block == 2)
# 
# # Block 3
# ds_sst_3 <- ds_sst |>
#   filter(block == 3)
# 
# # Combined
# ds_sst_com <- ds_sst |>
#   filter(block == 2 | block == 3)
# 
# head(ds_sst_1)
```

## Scoring the SRT
```{r}
# fn_score <- function(ds) { 
#   # Mean SSD
#   mean_ssd <- mean(ds[ds$condition == 1, ]$ssd)
#   # Proportion of failed nogos
#   p_failed_nogo <- 1 - mean(ds[ds$condition == 1, ]$response)
#   # Go RTs
#   go_rts <- ds[
#     ds$condition == 0 &
#       ds$rt > 0,
#     ]$rt
#   # n-th percentile of Go RTs
#   rt_quantile <- quantile(go_rts, p_failed_nogo, names = FALSE)
#   # SSRTi
#   return(rt_quantile - mean_ssd)
# }
```
## KEY

Regarding restructuring the data into wide format and cleaning the data, this is what we need:

Participant number
Mean Block 1 GoRT
Block 1 Go Trials Correct
Block 1 Stop Trials correct
Block 1 SSRT
Mean Block 2 GoRT
Block 2 Go Trials Correct
Block 2 Stop Trials correct
Block 2 SSRT
Mean Block 3 GoRT
Block 3 Go Trials Correct
Block 3 Stop Trials correct
Block 3 SSRT
Combined Mean Block 2 + Block 3 GoRT
Combined Block 2 + Block 3 Go Trials Correct
Combined Block 2 + Block 3 Stop trials correct
Combined Block 2 + Block 3 SSRT
Slider Value for RSDI on each image type

Block Go vs Stop Trials
Block 1 = 150 Go, 50 Stop
Block 2 = 78 Go, 26 Stop
Block 2 = 78 Go, 26 Stop

KEY
Subject = Participant number
Trial Type = BkGg (Black = Go trial, Red = Stop trial)
GoAcc = Correct Go Response (1 = correct, 0 = incorrect)
Go.RT = Go Reaction Time 
GoDur = Stop Signal Delay (SSD)
Go1s.ACC = Correct Stoppage (1 = correct, 0 = incorrect)
Block = Running[Block] (Block 1, Block 2, Block 3)
Slider Values for negative image = NegDistress.Slider1.Value, NegUpsetSlider1.Value
Slider Values for neutral image = NeuDistress.Slider1.Value, NeuUpsetSlider1.Value
Slider Values for positive image = PosDistress.Slider1.Value, PosUpsetSlider1.Value
Slider Values for trauma images = every slider value that begins with "Trauma1" or "Trauma2". There should be 11 sliders for each trauma picture

```{r}
# # Participant number
# participant <- df[1,1]
# 
# 
# ### Block 1 ###
# # Mean Block 1 GoRT
# B1_Mean_GoRT = mean(block1$Go.RT, na.rm = TRUE)
# # Block 1 Go Trials Correct
# B1_Go_ACC = sum(block1$Go.ACC, na.rm = TRUE)
# # Block 1 Stop Trials correct
# B1_Stop_ACC = sum(block1$Go1s.ACC, na.rm = TRUE)
# # Block 1 SSRT
# B1_SSRT = fn_score(subset(ds_sst_1, participant == 952))
# 
# ### Block 2 ###
# # Mean Block 2 GoRT
# B2_Mean_GoRT = mean(block2$Go.RT, na.rm = TRUE)
# # Block 2 Go Trials Correct
# B2_Go_ACC = sum(block2$Go.ACC, na.rm = TRUE)
# # Block 2 Stop Trials correct
# B2_Stop_ACC = sum(block2$Go1s.ACC, na.rm = TRUE)
# # Block 2 SSRT
# B2_SSRT = fn_score(subset(ds_sst_2, participant == 952))
# 
# ### Block 3 ###
# # Mean Block 3 GoRT
# B3_Mean_GoRT = mean(block3$Go.RT, na.rm = TRUE)
# # Block 3 Go Trials Correct
# B3_Go_ACC = sum(block3$Go.ACC, na.rm = TRUE)
# # Block 3 Stop Trials correct
# B3_Stop_ACC = sum(block3$Go1s.ACC, na.rm = TRUE)
# # Block 3 SSRT
# B3_SSRT = fn_score(subset(ds_sst_3, participant == 952))
# 
# ### Combined Stuff
# # Combined Mean Block 2 + Block 3 GoRT
# Combined_Mean_GoRT = mean(combined$Go.RT, na.rm = TRUE)
# # Combined Block 2 + Block 3 Go Trials Correct
# Combined_Go_ACC = sum(combined$Go.ACC, na.rm = TRUE)
# # Combined Block 2 + Block 3 Stop trials correct
# Combined_Stop_ACC = sum(combined$Go1s.ACC, na.rm = TRUE)
# # Combined Block 2 + Block 3 SSRT
# Combined_SSRT = fn_score(subset(ds_sst_com, participant == 952))
# 
# ### Slider stuff###
# # Slider Value for RSDI on each image type
# # Trial 1
# NegDistress     = Emotion$NegDistress[1]
# NegUpset        = Emotion$NegUpset[1]
# 
# # Trial 2
# NeuDistress     = Emotion$NeuDistress[2]
# NeuUpset        = Emotion$NeuUpset[2]
# 
# # Trial 3
# PosDistress     = Emotion$PosDistress[3]
# PosUpset        = Emotion$PosUpset[3]
# 
# #Trial 4
# Derealiz        = Emotion$Derealiz[4] 
# Dissoc          = Emotion$Dissoc[4]
# Emot_Avoid      = Emotion$Emot_Avoid[4] 
# 
# # Trial 5
# CogAvoi         = Emotion$CogAvoi[5]
# Deperson        = Emotion$Deperson[5] 
# CogAvoi         = Emotion$CogAvoi[5] 
# Trauma_Distress = Emotion$Trauma_Distress[5] 

```


## combine into one data frame (row)
```{r}
# output_data = data.frame(
#     participant, 
#     B1_Mean_GoRT, B1_Go_ACC, B1_Stop_ACC,B1_SSRT,
#     B2_Mean_GoRT, B2_Go_ACC, B2_Stop_ACC,B2_SSRT,
#     B3_Mean_GoRT, B3_Go_ACC, B3_Stop_ACC,B3_SSRT,
#     Combined_Mean_GoRT, Combined_Go_ACC, Combined_Stop_ACC,Combined_SSRT,
#     NegDistress, NegUpset, NeuDistress,NeuUpset, PosDistress, PosUpset, CogAvoi, Deperson, Derealiz, Dissoc, CogAvoi, Trauma_Distress, Emot_Avoid 
# )
# 
# 
# filename = paste0("~/Downloads/S",part_num,"_SSRT.csv")
# write.csv(output_data, filename)


```

## combine into one data frame (row)
```{r}
# output_data = data.frame(
#     participant, 
#     B1_Mean_GoRT, B1_Go_ACC, B1_Stop_ACC,B1_SSRT,
#     B2_Mean_GoRT, B2_Go_ACC, B2_Stop_ACC,B2_SSRT,
#     B3_Mean_GoRT, B3_Go_ACC, B3_Stop_ACC,B3_SSRT,
#     Combined_Mean_GoRT, Combined_Go_ACC, Combined_Stop_ACC,Combined_SSRT,
#     NegDistress, NegUpset, NeuDistress,NeuUpset, PosDistress, PosUpset, CogAvoi, Deperson, Derealiz, Dissoc, CogAvoi, Trauma_Distress, Emot_Avoid 
# )
# filename = paste0("~/Downloads/S",part_num,"_SSRT.csv")
# write.csv(output_data, filename)
```



##Drop the first trial
maybe?
```{r}
# ds_tab <- ds_sst_1[-1,]
# ds_1 <- subset(ds_tab, participant  == 952)
# table(ds_1$condition)
```

## Scoring the SRT
```{r}
# fn_score <- function(ds) { 
#   # Mean SSD
#   mean_ssd <- mean(ds[ds$condition == 1, ]$ssd)
#   # Proportion of failed nogos
#   p_failed_nogo <- 1 - mean(ds[ds$condition == 1, ]$response)
#   # Go RTs
#   go_rts <- ds[
#     ds$condition == 0 &
#       ds$rt > 0,
#     ]$rt
#   # n-th percentile of Go RTs
#   rt_quantile <- quantile(go_rts, p_failed_nogo, names = FALSE)
#   # SSRTi
#   return(rt_quantile - mean_ssd)
# }
```

Scoring a particiapnt 
```{r}
# fn_score(subset(ds_sst_1.2, participant == 952))
```

Scoring everyone
```{r}
# scores <- by(
#   ds_sst,
#   ds_sst$participant,
#   fn_score
# )
# SSRT_DF<- data.frame(
#       participant = names(scores),
#       score = as.vector(scores)
# )
# 
# SSRT_DF[1:10,]
```

