---
title: "Data_Import"
output: html_document
date: "2023-07-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE)

library(readxl)
library(tidyverse)
library(dplyr)
library(haven)
library(stringr)
```

Read in data
```{r}
#read in files
# data1 <- read_excel("~/Downloads/test1.xlsx") #, col_names = TRUE)
# data2 <- read_excel("~/Downloads/test2.xlsx")#, col_names = TRUE)
# Excel69420 <- read_excel("~/Downloads/69420Excel.xlsx", col_names = TRUE)
```


```{r}
Output_df <- NA

df <- block2

## library(SSRTcalc)

SSRT_adapt <- function(df){
  go_trials = df[ which(df$condition == 0),]
  stop_trials <- df[ which(df$condition==1), ]
  stop_count <- sum(stop_trials$response)
  overall_prob = 1 - stop_count/nrow(stop_trials)
  df1 <- go_trials[order(go_trials$react_time, na.last = NA), ]
  the_order <- order(go_trials$react_time, na.last = NA)
  nrt <- length(df$react_time)
  nthindex = as.integer(round(nrt*overall_prob))
  meanssd = mean(stop_trials$ssd, na.rm =TRUE)
  nthrt <- df1$react_time[nthindex]
  ssrt_raw <- nthrt - meanssd
  ssrt_raw
  return(ssrt_raw)
}

view(df1)

```

## KEY
- Subject = Participant number
- Trial Type = BkGg (Black = Go trial, Red = Stop trial)
- GoAcc = Correct Go Response (1 = correct, 0 = incorrect)
- Go.RT = Go Reaction Time 
- GoDur = Stop Signal Delay (SSD)
- Inhs.ACC = Correct Stoppage (1 = correct, 0 = incorrect)
- Block = Running[Block] (Block 1, Block 2, Block 3)
- Slider Values for negative image = NegDistress.Slider1.Value, NegUpsetSlider1.Value
- Slider Values for neutral image = NeuDistress.Slider1.Value, NeuUpsetSlider1.Value
- Slider Values for positive image = PosDistress.Slider1.Value, PosUpsetSlider1.Value
- Slider Values for trauma images = every slider value that begins with "Trauma1" or "Trauma2". There should be 11 sliders for each trauma picture

```{r}
# length("~/Desktop/Coding/data/SSRT/")


# dir.create("~/Downloads/Neutral_Images")

# files <- list.files(path = "~/Desktop/Coding/data/SSRT", pattern = "\\.csv$", full.names = TRUE)
# length_of_files = length(files)

files <- list.files(path = "~/Downloads/SSRT", pattern = "\\.csv$", full.names = TRUE)
length_of_files = length(files)
```


```{r}
#################
# output = NA ## might not need?? 

#2. specify variable names
df_names = c("Subject", "B1_Mean_GoRT", "B1_Go_ACC", "B1_Stop_ACC",    
             "B1_mean_SSRT", "B1_mean_failed_RT", "B1_mean_ssd", "B2_Mean_GoRT",
             "B2_Go_ACC", "B2_Stop_ACC", "B2_mean_SSRT", "B2_mean_failed_RT",  
             "B2_mean_ssd", "B3_Mean_GoRT", "B3_Go_ACC", "B3_Stop_ACC",
             "B3_mean_SSRT", "B3_mean_failed_RT", "B3_mean_ssd" , "Combined_Mean_GoRT",
             "Combined_Go_ACC", "Combined_Stop_ACC",  "Combined_mean_SSRT", "Combined_mean_failed_RT",
             "Combined_mean_ssd", "NegDistress", "NegUpset", "NeuDistress",
             "NeuUpset", "PosDistress", "PosUpset", "CogAvoi",
             "Deperson", "Derealiz", "Dissoc", "Trauma_Distress", 
             "EmotAvoi", "Fog", "PhysAvoi", "PhysRx",  "Reexp",  "Trauma_Upset", "CogAvoi_2", 
             "Deperson_2", "Derealiz_2", "Dissoc_2", "CogAvoi_2", "Trauma_Distress_2", "EmotAvoi_2", 
             "Fog_2", "PhysAvoi_2", "PhysRx_2", "Reexp_2", "Trauma_Upset_2"
             )
#1. create dataframe for the for data
df_output = data.frame(matrix(ncol = length(df_names),nrow = 0))
#assign variable names to df_output 
names(df_output) = df_names
df_output

```

run for loop to extract files.
```{r}
for(i in 1:length(files)){
## Read in data  
data <- read_csv(files[i])
  ## Prepping DF for analyses
#1. Correct the column headers
  head <- data[1,]
  colnames(data) = head
  data <- data[-1,]
  ds_sst <- NA
#2. select and create the new variables we need and put those into a new df 
  df <- data %>%
    select(
             #overall stuff
             Subject, Group, Block, SessionDate, SessionStartDateTimeUtc,GoCorrect:InitGoRT,
             PercentStop,StopCorr,Trial,BkGd,GoDur,
             #distress/ upset sliders
             NegDistress.Slider1.Value, NegUpset.Slider1.Value,
             NeuDistress.Slider1.Value, NeuUpset.Slider1.Value,
             PosDistress.Slider1.Value, PosUpset.Slider1.Value, 
             #RTstuff
             CorrectAnswer, EmotionalPic,Go.ACC,Go.DurationError,Go.OnsetTime,Go.RT, 
             Inhs.ACC, Inhs.RT,
             # trauma 1
             Trauma1CogAvoi.Slider1.Value, 
             Trauma1Deperson.Slider1.Value,     
             Trauma1Derealiz.Slider1.Value, 
             Trauma1Dissoc.Slider1.Value, 
             Trauma1Distress.Slider1.Value, 
             Trauma1EmotAvoi.Slider1.Value,
             Trauma1Fog.Slider1.Value,
             Trauma1PhysAvoi.Slider1.Value,
             Trauma1PhysRx.Slider1.Value,
             Trauma1Reexp.Slider1.Value,
             Trauma1Upset.Slider1.Value,
             #trauma 2
             Trauma1CogAvoi1.Slider1.Value, 
             Trauma1Deperson1.Slider1.Value,     
             Trauma1Derealiz1.Slider1.Value, 
             Trauma1Dissoc1.Slider1.Value, 
             Trauma1CogAvoi1.Slider1.Value, 
             Trauma1Distress1.Slider1.Value, 
             Trauma1EmotAvoi1.Slider1.Value,
             Trauma1Fog1.Slider1.Value,
             Trauma1PhysAvoi1.Slider1.Value,
             Trauma1PhysRx1.Slider1.Value,
             Trauma1Reexp1.Slider1.Value,
             Trauma1Upset1.Slider1.Value,
             ) %>%
             # 
    mutate(
             Subject = as.double(Subject),
             Group = as.factor(Group),
             Block =as.factor(Block),
             # `Running[Block]` = as.factor(`Running[Block]`),
             Trial = factor(Trial),
             BkGd = as.factor(BkGd),
             Go_Stop_Trial = ifelse(BkGd == "Black", "Go",
                             ifelse(BkGd == "Red", "Stop", NA
                                    )),
            GoDur = as.double(GoDur),
            Go.ACC = as.double(Go.ACC),
            Inhs.ACC = as.double(Inhs.ACC),
            Go.RT = as.double(Go.RT),
            NegDistress = as.double(NegDistress.Slider1.Value),
            NegUpset = as.double(NegUpset.Slider1.Value),
            NeuDistress = as.double(NeuDistress.Slider1.Value),
            NeuUpset = as.double(NeuUpset.Slider1.Value),
            PosDistress = as.double(PosDistress.Slider1.Value),
            PosUpset = as.double(PosUpset.Slider1.Value),
            CogAvoi  = as.double(Trauma1CogAvoi.Slider1.Value),
            Deperson = as.double(Trauma1Deperson.Slider1.Value),    
            Derealiz = as.double(Trauma1Deperson.Slider1.Value),
            Dissoc = as.double(Trauma1Dissoc.Slider1.Value),
            Trauma_Distress = as.double(Trauma1Distress.Slider1.Value),
            EmotAvoi = as.double(Trauma1EmotAvoi.Slider1.Value),
            Fog = as.double(Trauma1Fog.Slider1.Value),
            PhysAvoi = as.double(Trauma1PhysAvoi.Slider1.Value),
            PhysRx = as.double(Trauma1PhysRx.Slider1.Value),
            Reexp = as.double(Trauma1Reexp.Slider1.Value),
            Trauma_Upset = as.double(Trauma1Upset.Slider1.Value),
            CogAvoi_2 = as.double(Trauma1CogAvoi1.Slider1.Value),
            Deperson_2 = as.double(Trauma1Deperson1.Slider1.Value),
            Derealiz_2 = as.double(Trauma1Derealiz1.Slider1.Value),
            Dissoc_2 = as.double(Trauma1Dissoc1.Slider1.Value),
            Trauma_Distress_2 = as.double(Trauma1Distress1.Slider1.Value),
            EmotAvoi_2 = as.double(Trauma1EmotAvoi1.Slider1.Value),
            Fog_2 = as.double(Trauma1Fog1.Slider1.Value),
            PhysAvoi_2 = as.double(Trauma1PhysAvoi1.Slider1.Value),
            PhysRx_2 = as.double(Trauma1PhysRx1.Slider1.Value),
            Reexp_2 = as.double(Trauma1Reexp1.Slider1.Value),
            Trauma_Upset_2 = as.double(Trauma1Upset1.Slider1.Value)
    )
  
  
#3. Create new df used for SSRT analyses / wide data

ssrt_df <- df %>%
      mutate(
        participant = Subject,
        block = Block,
        block = ifelse(Block == "1", 0,
                ifelse(Block == "2", 1,
                ifelse(Block == "4", 2,
                ifelse(Block == "6", 3,
                ifelse(Block == "8", 4, NA
                       ))))),
        ssd = GoDur,
        #go or stop trial 
        condition = ifelse(Go_Stop_Trial == "Go", 0,
                    ifelse(Go_Stop_Trial == "Stop", 1,NA
                           )),
        #correct response 
        response = ifelse(Go.ACC == 1 | Inhs.ACC == 1, 1, 0),
        response = ifelse(is.na(response), 0, response
                                    ),
        trial = Trial,
        #reaction time 
        react_time = as.double(
          #block 1
          ifelse(Block == 2 & BkGd == "Black" & Go.ACC == 0 & (is.na(Go.RT) | Go.RT == 0),
            max(df$Go.RT[which(df$Block==2)], na.rm = TRUE),
          #block 1
          ifelse(Block == 4 & BkGd == "Black" & Go.ACC == 0 & (is.na(Go.RT) | Go.RT == 0),
            max(df$Go.RT[which(df$Block==4)], na.rm = TRUE),
          #block 1
          ifelse(Block == 6 & BkGd == "Black" & Go.ACC == 0 & (is.na(Go.RT) | Go.RT == 0),
            max(df$Go.RT[which(df$Block==6)], na.rm = TRUE),Go.RT)))),
        block = as.integer(block),
        trial = as.integer(trial),
        ssd = as.double(ssd),
        condition = as.integer(condition),
        response = as.integer(response),
        participant = as.integer(participant),
        Failed_stop_time = 
          ifelse(Inhs.ACC == 0, as.double(Inhs.RT), NA
          ),
        Failed_stop_time = as.double(Failed_stop_time)
        ) |>
    filter(
      !is.na(Trial)
    )

ssrt_df %>% 
  group_by(Block, BkGd) %>%
  filter(BkGd == "Black") %>% 
  arrange(react_time) %>% 
  select(Go.ACC, react_time)

## extract number of missed go trials that were replaced.
  b1_missed_go <- unlist(
  ssrt_df %>% 
  filter(
    Block == 2,
    BkGd == "Black"
  ) %>% 
  select(
    Go.ACC
  ) %>% 
  summarise(block1_missed = length(Go.ACC)- sum(Go.ACC))
)

b2_missed_go <- unlist(ssrt_df %>% 
  filter(
    Block == 4,
    BkGd == "Black"
  ) %>% 
  select(
    Go.ACC
  ) %>% 
  summarise(block2_missed = length(Go.ACC)- sum(Go.ACC))
)

b3_missed_go <- unlist(ssrt_df %>% 
  filter(
    Block == 6,
    BkGd == "Black"
  ) %>% 
  select(
    Go.ACC
  ) %>% 
  summarise(block3_missed = length(Go.ACC)- sum(Go.ACC))
)

ssrt_df <- ssrt_df %>% 
  mutate(
    b1_missed_go = b1_missed_go,
    b2_missed_go = b2_missed_go,
    b3_missed_go = b3_missed_go
  )
  
#4. Assign values of each block to their own df
    block1 <- ssrt_df  %>%
      filter(Block == "2")
    block2 <- ssrt_df  %>%
      filter(Block == "4")
    block3 <- ssrt_df  %>%
      filter(Block == "6")
    combined <- ssrt_df  %>%
      filter(Block == "4" | Block == "6")
    Emotion <- ssrt_df  %>%
      filter(Block == "8")
 # ssrt_df$block

## Prepping data for SSRT stuff
#1. Create a new df that is in the specific order for the SSRT function
ds_sst <- ssrt_df %>% 
  dplyr::select(
    'block', 'trial', 'ssd', 'condition', 'response','react_time','participant'
    ) |>
  filter(!is.na(trial))

# Block 1
ds_sst_1 <- ds_sst |>
  filter(block == 1)

# Block 2
ds_sst_2 <- ds_sst |>
  filter(block == 2)

# Block 3
ds_sst_3 <- ds_sst |>
  filter(block == 3)

# Combined
ds_sst_com <- ds_sst |>
  filter(block == 2 | block == 3)

## Pull out the information for the wide
#1. Participant number

participant<- df[1,1]

#2. Block 1 ---------------

# Mean Block 1 GoRT
B1_Mean_GoRT = mean(block1$react_time, na.rm = TRUE)
 # block 1 mean ssd
B1_mean_ssd = mean(block1$ssd,na.rm = TRUE)
# Block 1 Go Trials Correct
B1_Go_ACC = sum(block1$Go.ACC, na.rm = TRUE)
# Block 1 Stop Trials correct
B1_Stop_ACC = sum(block1$Inhs.ACC, na.rm = TRUE)
# Block 1  (MeanGoRT - MeanSSD)
B1_mean_SSRT = B1_Mean_GoRT - mean(block1$ssd, na.rm = TRUE)
#   Block 1 Failed Mean Stop RT
B1_mean_failed_RT = mean(block1$Failed_stop_time,na.rm = TRUE)
# SSRT Please
B1_SSRT_adapt = SSRT_adapt(ds_sst_1)

#3. Block 2 ---------------

# Mean Block 2 GoRT
B2_Mean_GoRT = mean(block2$react_time, na.rm = TRUE)
# Block 2 Go Trials Correct
B2_Go_ACC = sum(block2$Go.ACC, na.rm = TRUE)
# Block 2 Stop Trials correct
B2_Stop_ACC = sum(block2$Inhs.ACC, na.rm = TRUE)
# Block 2  (MeanGoRT - MeanSSD)
B2_mean_SSRT = B2_Mean_GoRT - mean(block2$ssd, na.rm = TRUE)
#   Block 3 Block 3 Failed Mean Stop RT
B2_mean_failed_RT = mean(block2$Failed_stop_time,na.rm = TRUE)
 # block 2 mean ssd
B2_mean_ssd = mean(block2$ssd,na.rm = TRUE)
# SSRT Please
B2_SSRT_adapt = SSRT_adapt(ds_sst_2)

#4. Block 3 -----------------
# Mean Block 3 GoRT
B3_Mean_GoRT = mean(block3$react_time, na.rm = TRUE)
# Block 3 Go Trials Correct
B3_Go_ACC = sum(block3$Go.ACC, na.rm = TRUE)
# Block 3 Stop Trials correct
B3_Stop_ACC = sum(block3$Inhs.ACC, na.rm = TRUE)
# Block 3  (MeanGoRT - MeanSSD)
B3_mean_SSRT = B3_Mean_GoRT - mean(block3$ssd, na.rm = TRUE)
#   Block 3 Block 3 Failed Mean Stop RT
B3_mean_failed_RT = mean(block3$Failed_stop_time,na.rm = TRUE)
 # block 3 mean ssd
B3_mean_ssd = mean(block3$ssd,na.rm = TRUE)
# B3_SSRT
B3_SSRT_adapt = SSRT_adapt(ds_sst_3)

#5. Combined Stuff ----------------
# Combined Mean Block 2 + Block 3 GoRT
Combined_Mean_GoRT = mean(combined$react_time, na.rm = TRUE)
# Combined Block 2 + Block 3 Go Trials Correct
Combined_Go_ACC = sum(combined$Go.ACC, na.rm = TRUE)
# Combined Block 2 + Block 3 Stop trials correct
Combined_Stop_ACC = sum(combined$Inhs.ACC, na.rm = TRUE)
# Combined Block 2 + (MeanGoRT - MeanSSD)
Combined_mean_SSRT = Combined_Mean_GoRT - mean(combined$ssd, na.rm = TRUE)
# Combined Block 2 + Block 3 Block 3 Failed Mean Stop RT
Combined_mean_failed_RT =mean(combined$Failed_stop_time,na.rm = TRUE)
 # combined mean ssd
Combined_mean_ssd = mean(combined$ssd,na.rm = TRUE)
# combined_SSRT
Combined_SSRT_adapt = SSRT_adapt(combined)

#6. Slider stuff ------------------
# Slider Value for RSDI on each image type
# Trial 1
NegDistress     = Emotion$NegDistress[!is.na(Emotion$NegDistress)]
NegUpset        = Emotion$NegUpset[!is.na(Emotion$NegUpset)]

# Trial 2
NeuDistress     = Emotion$NeuDistress[!is.na(Emotion$NeuDistress)]
NeuUpset        = Emotion$NeuUpset[!is.na(Emotion$NeuUpset)]

# Trial 3
PosDistress     = Emotion$PosDistress[!is.na(Emotion$PosDistress)]
PosUpset        = Emotion$PosUpset[!is.na(Emotion$PosUpset)]

# #Trauma 1
# Derealiz        = Emotion$Derealiz[!is.na(Emotion$Derealiz)] 
# Dissoc          = Emotion$Dissoc[!is.na(Emotion$Dissoc)] 
# Emot_Avoid      = Emotion$Emot_Avoid[!is.na(Emotion$Emot_Avoid)] 

#trauma 1
CogAvoi         = df$CogAvoi[!is.na(df$CogAvoi)]
Deperson        = df$Deperson[!is.na(df$Deperson)]
Derealiz        = df$Derealiz[!is.na(df$Derealiz)] 
Dissoc          = df$Dissoc[!is.na(df$Dissoc)] 
Trauma_Distress = df$Trauma_Distress[!is.na(df$Trauma_Distress)] 
EmotAvoi        = df$EmotAvoi[!is.na(df$EmotAvoi)] 
Fog             = df$Fog[!is.na(df$Fog)]
PhysAvoi        = df$PhysAvoi[!is.na(df$PhysAvoi)]
PhysRx          = df$PhysRx[!is.na(df$PhysRx)]
Reexp           = df$Reexp[!is.na(df$Reexp)]
Trauma_Upset    = df$Trauma_Upset[!is.na(df$Trauma_Upset)]
CogAvoi_2       = df$CogAvoi_2[!is.na(df$CogAvoi_2)]
Deperson_2      = df$Deperson_2[!is.na(df$Deperson_2)]
Derealiz_2      = df$Derealiz_2[!is.na(df$Derealiz_2)]
Dissoc_2        = df$Dissoc_2[!is.na(df$Dissoc_2)]
Trauma_Distress_2 = df$Trauma_Distress_2[!is.na(df$Trauma_Distress_2)]
EmotAvoi_2      = df$EmotAvoi_2[!is.na(df$EmotAvoi_2)]
Fog_2           = df$Fog_2[!is.na(df$Fog_2)]
PhysAvoi_2      = df$PhysAvoi_2[!is.na(df$PhysAvoi_2)]
PhysRx_2        = df$PhysRx_2[!is.na(df$PhysRx_2)]
Reexp_2         = df$Reexp_2[!is.na(df$Reexp_2)]
Trauma_Upset_2  = df$Trauma_Upset_2[!is.na(df$Trauma_Upset_2)]

## combine into one data frame (row)

output_data = data.frame(
    participant,
    B1_Mean_GoRT, B1_mean_ssd, B1_mean_SSRT, B1_SSRT_adapt, 
    B1_Go_ACC, B1_Stop_ACC, B1_mean_failed_RT, 
    B2_Mean_GoRT, B2_mean_ssd, B2_mean_SSRT, B2_SSRT_adapt,
    B2_Go_ACC, B2_Stop_ACC, B2_mean_failed_RT,
    B3_Mean_GoRT, B3_mean_ssd, B3_mean_SSRT, B3_SSRT_adapt, 
    B3_Go_ACC, B3_Stop_ACC, B3_mean_failed_RT,
    Combined_Mean_GoRT, Combined_mean_ssd, Combined_mean_SSRT, Combined_SSRT_adapt,     
    Combined_Go_ACC, Combined_Stop_ACC, Combined_mean_failed_RT,
    NegDistress, NegUpset, NeuDistress, NeuUpset, PosDistress, PosUpset,
    CogAvoi, Deperson, Derealiz, Dissoc, Trauma_Distress, EmotAvoi,
    Fog,  PhysAvoi, PhysRx, Reexp, Trauma_Upset,
    CogAvoi_2, Deperson_2, Derealiz_2, Dissoc_2, Trauma_Distress_2,
    EmotAvoi_2, Fog_2, PhysAvoi_2, PhysRx_2, Reexp_2,Trauma_Upset_2
)

df_output <- rbind(df_output,output_data)
view(df_output)
}

df_output

write_csv(df_output,"~/Downloads/METRIC_DATA.csv")
```

```{r,include=FALSE}
# write_sav(df_output,"~/Downloads/METRIC_DATA.sav")
data <- read_csv("~/Downloads/SST_Task-43-1.csv")
  ## Prepping DF for analyses
#1. Correct the column headers
  head <- data[1,]
  colnames(data) = head
  data <- data[-1,]
  ds_sst <- NA
#2. select and create the new variables we need and put those into a new df 
  df <- data %>%
    select(
             #overall stuff
             Subject, Group, Block, SessionDate, SessionStartDateTimeUtc,GoCorrect:InitGoRT,
             PercentStop,StopCorr,Trial,BkGd,GoDur,
             #distress/ upset sliders
             NegDistress.Slider1.Value, NegUpset.Slider1.Value,
             NeuDistress.Slider1.Value, NeuUpset.Slider1.Value,
             PosDistress.Slider1.Value, PosUpset.Slider1.Value, 
             #RTstuff
             CorrectAnswer, EmotionalPic,Go.ACC,Go.DurationError,Go.OnsetTime,Go.RT, 
             Inhs.ACC, Inhs.RT,
             # trauma 1
             Trauma1CogAvoi.Slider1.Value, 
             Trauma1Deperson.Slider1.Value,     
             Trauma1Derealiz.Slider1.Value, 
             Trauma1Dissoc.Slider1.Value, 
             Trauma1Distress.Slider1.Value, 
             Trauma1EmotAvoi.Slider1.Value,
             Trauma1Fog.Slider1.Value,
             Trauma1PhysAvoi.Slider1.Value,
             Trauma1PhysRx.Slider1.Value,
             Trauma1Reexp.Slider1.Value,
             Trauma1Upset.Slider1.Value,
             #trauma 2
             Trauma1CogAvoi1.Slider1.Value, 
             Trauma1Deperson1.Slider1.Value,     
             Trauma1Derealiz1.Slider1.Value, 
             Trauma1Dissoc1.Slider1.Value, 
             Trauma1CogAvoi1.Slider1.Value, 
             Trauma1Distress1.Slider1.Value, 
             Trauma1EmotAvoi1.Slider1.Value,
             Trauma1Fog1.Slider1.Value,
             Trauma1PhysAvoi1.Slider1.Value,
             Trauma1PhysRx1.Slider1.Value,
             Trauma1Reexp1.Slider1.Value,
             Trauma1Upset1.Slider1.Value,
             ) %>%
             # 
    mutate(
             Subject = as.double(Subject),
             Group = as.factor(Group),
             Block =as.factor(Block),
             # `Running[Block]` = as.factor(`Running[Block]`),
             Trial = factor(Trial),
             BkGd = as.factor(BkGd),
             Go_Stop_Trial = ifelse(BkGd == "Black", "Go",
                             ifelse(BkGd == "Red", "Stop", NA
                                    )),
            GoDur = as.double(GoDur),
            Go.ACC = as.double(Go.ACC),
            Inhs.ACC = as.double(Inhs.ACC),
            Go.RT = as.double(Go.RT),
            NegDistress = as.double(NegDistress.Slider1.Value),
            NegUpset = as.double(NegUpset.Slider1.Value),
            NeuDistress = as.double(NeuDistress.Slider1.Value),
            NeuUpset = as.double(NeuUpset.Slider1.Value),
            PosDistress = as.double(PosDistress.Slider1.Value),
            PosUpset = as.double(PosUpset.Slider1.Value),
            CogAvoi  = as.double(Trauma1CogAvoi.Slider1.Value),
            Deperson = as.double(Trauma1Deperson.Slider1.Value),    
            Derealiz = as.double(Trauma1Deperson.Slider1.Value),
            Dissoc = as.double(Trauma1Dissoc.Slider1.Value),
            Trauma_Distress = as.double(Trauma1Distress.Slider1.Value),
            EmotAvoi = as.double(Trauma1EmotAvoi.Slider1.Value),
            Fog = as.double(Trauma1Fog.Slider1.Value),
            PhysAvoi = as.double(Trauma1PhysAvoi.Slider1.Value),
            PhysRx = as.double(Trauma1PhysRx.Slider1.Value),
            Reexp = as.double(Trauma1Reexp.Slider1.Value),
            Trauma_Upset = as.double(Trauma1Upset.Slider1.Value),
            CogAvoi_2 = as.double(Trauma1CogAvoi1.Slider1.Value),
            Deperson_2 = as.double(Trauma1Deperson1.Slider1.Value),
            Derealiz_2 = as.double(Trauma1Derealiz1.Slider1.Value),
            Dissoc_2 = as.double(Trauma1Dissoc1.Slider1.Value),
            Trauma_Distress_2 = as.double(Trauma1Distress1.Slider1.Value),
            EmotAvoi_2 = as.double(Trauma1EmotAvoi1.Slider1.Value),
            Fog_2 = as.double(Trauma1Fog1.Slider1.Value),
            PhysAvoi_2 = as.double(Trauma1PhysAvoi1.Slider1.Value),
            PhysRx_2 = as.double(Trauma1PhysRx1.Slider1.Value),
            Reexp_2 = as.double(Trauma1Reexp1.Slider1.Value),
            Trauma_Upset_2 = as.double(Trauma1Upset1.Slider1.Value)
    )
  
#3. Create new df used for SSRT analyses / wide data
  ssrt_df <- df %>%
      mutate(
        participant = Subject,
        block = Block,
        block = ifelse(Block == "1", 0,
                ifelse(Block == "3", 1,
                ifelse(Block == "5", 2,
                ifelse(Block == "7", 3,
                ifelse(Block == "9", 4, NA
                       ))))),
        ssd = GoDur,
        #go or stop trial 
        condition = ifelse(Go_Stop_Trial == "Go", 0,
                    ifelse(Go_Stop_Trial == "Stop", 1,NA
                           )),
        #correct response 
        response = ifelse(Go.ACC == 1 | Inhs.ACC == 1, 1, 0),
        response = ifelse(is.na(response), 0, response
                                    ),
        trial = Trial,
        #reaction time 
        react_time = as.double(
          #block 1
          ifelse(Block == 3 & BkGd == "Black" & Go.ACC == 0 & (is.na(Go.RT) | Go.RT == 0),
            max(df$Go.RT[which(df$Block==3)], na.rm = TRUE),
          #block 1
          ifelse(Block == 5 & BkGd == "Black" & Go.ACC == 0 & (is.na(Go.RT) | Go.RT == 0),
            max(df$Go.RT[which(df$Block==5)], na.rm = TRUE),
          #block 1
          ifelse(Block == 7 & BkGd == "Black" & Go.ACC == 0 & (is.na(Go.RT) | Go.RT == 0),
            max(df$Go.RT[which(df$Block==7)], na.rm = TRUE),Go.RT)))),
        block = as.integer(block),
        trial = as.integer(trial),
        ssd = as.double(ssd),
        condition = as.integer(condition),
        response = as.integer(response),
        participant = as.integer(participant),
        Failed_stop_time = 
          ifelse(Inhs.ACC == 0, as.double(Inhs.RT), NA
          ),
        Failed_stop_time = as.double(Failed_stop_time), 
        num_missed_gos = ifelse(
          Block == 3, sum(df$Go.ACC[which(df$BkGd == "Black")]), -999999
        )
        ) |>
    filter(
      !is.na(Trial)
    )

b1_missed_go <- unlist(
  ssrt_df %>% 
  filter(
    Block == 3,
    BkGd == "Black"
  ) %>% 
  select(
    Go.ACC
  ) %>% 
  summarise(block1_missed = length(Go.ACC)- sum(Go.ACC))
)

b2_missed_go <- unlist(ssrt_df %>% 
  filter(
    Block == 5,
    BkGd == "Black"
  ) %>% 
  select(
    Go.ACC
  ) %>% 
  summarise(block2_missed = length(Go.ACC)- sum(Go.ACC))
)

b3_missed_go <- unlist(ssrt_df %>% 
  filter(
    Block == 7,
    BkGd == "Black"
  ) %>% 
  select(
    Go.ACC
  ) %>% 
  summarise(block3_missed = length(Go.ACC)- sum(Go.ACC))
)

ssrt_df <- ssrt_df %>% 
  mutate(
    b1_missed_go = b1_missed_go,
    b2_missed_go = b2_missed_go,
    b3_missed_go = b3_missed_go
  )

#4. Assign values of each block to their own df
    block1 <- ssrt_df  %>%
      filter(Block == "3")
    block2 <- ssrt_df  %>%
      filter(Block == "5")
    block3 <- ssrt_df  %>%
      filter(Block == "7")
    combined <- ssrt_df  %>%
      filter(Block == "5" | Block == "7")
    Emotion <- ssrt_df  %>%
      filter(Block == "9")
    
 # ssrt_df$block   

## Prepping data for SSRT stuff
#1. Create a new df that is in the specific order for the SSRT function
ds_sst <- ssrt_df %>% 
  dplyr::select(
    'block', 'trial', 'ssd', 'condition', 'response','react_time','participant'
    ) |>
  filter(!is.na(trial))

# Block 1
ds_sst_1 <- ds_sst |>
  filter(block == 1)

# Block 2
ds_sst_2 <- ds_sst |>
  filter(block == 2)

# Block 3
ds_sst_3 <- ds_sst |>
  filter(block == 3)

# Combined
ds_sst_com <- ds_sst |>
  filter(block == 2 | block == 3)

## Pull out the information for the wide
#1. Participant number

participant<- df[1,1]

#2. Block 1 ---------------

# Mean Block 1 GoRT
B1_Mean_GoRT = mean(block1$react_time, na.rm = TRUE)
# Block 1 Go Trials Correct
B1_Go_ACC = sum(block1$Go.ACC, na.rm = TRUE)
# Block 1 Stop Trials correct
B1_Stop_ACC = sum(block1$Inhs.ACC, na.rm = TRUE)
# Block 1  (MeanGoRT - MeanSSD)
B1_mean_SSRT = B1_Mean_GoRT - mean(block1$ssd, na.rm = TRUE)
#   Block 1 Failed Mean Stop RT
B1_mean_failed_RT = mean(block1$Failed_stop_time,na.rm = TRUE)
 # block 1 mean ssd
B1_mean_ssd = mean(block1$ssd,na.rm = TRUE)
# SSRT Please
B1_SSRT_adapt = SSRT_adapt(ds_sst_1)

#3. Block 2 ---------------
# Mean Block 2 GoRT
B2_Mean_GoRT = mean(block2$react_time, na.rm = TRUE)
# Block 2 Go Trials Correct
B2_Go_ACC = sum(block2$Go.ACC, na.rm = TRUE)
# Block 2 Stop Trials correct
B2_Stop_ACC = sum(block2$Inhs.ACC, na.rm = TRUE)
# Block 2  (MeanGoRT - MeanSSD)
B2_mean_SSRT = B2_Mean_GoRT - mean(block2$ssd, na.rm = TRUE)
#   Block 3 Block 3 Failed Mean Stop RT
B2_mean_failed_RT = mean(block2$Failed_stop_time,na.rm = TRUE)
 # block 2 mean ssd
B2_mean_ssd = mean(block2$ssd,na.rm = TRUE)
# SSRT Please
B2_SSRT_adapt = SSRT_adapt(ds_sst_2)

#4. Block 3 -----------------
# Mean Block 3 GoRT
B3_Mean_GoRT = mean(block3$react_time, na.rm = TRUE)
# Block 3 Go Trials Correct
B3_Go_ACC = sum(block3$Go.ACC, na.rm = TRUE)
# Block 3 Stop Trials correct
B3_Stop_ACC = sum(block3$Inhs.ACC, na.rm = TRUE)
# Block 3  (MeanGoRT - MeanSSD)
B3_mean_SSRT = B3_Mean_GoRT - mean(block3$ssd, na.rm = TRUE)
#   Block 3 Block 3 Failed Mean Stop RT
B3_mean_failed_RT = mean(block3$Failed_stop_time,na.rm = TRUE)
 # block 3 mean ssd
B3_mean_ssd = mean(block3$ssd,na.rm = TRUE)
# B3_SSRT
B3_SSRT_adapt = SSRT_adapt(ds_sst_3)

#5. Combined Stuff ----------------
# Combined Mean Block 2 + Block 3 GoRT
Combined_Mean_GoRT = mean(combined$react_time, na.rm = TRUE)
# Combined Block 2 + Block 3 Go Trials Correct
Combined_Go_ACC = sum(combined$Go.ACC, na.rm = TRUE)
# Combined Block 2 + Block 3 Stop trials correct
Combined_Stop_ACC = sum(combined$Inhs.ACC, na.rm = TRUE)
# Combined Block 2 + (MeanGoRT - MeanSSD)
Combined_mean_SSRT = Combined_Mean_GoRT - mean(combined$ssd, na.rm = TRUE)
# Combined Block 2 + Block 3 Block 3 Failed Mean Stop RT
Combined_mean_failed_RT =mean(combined$Failed_stop_time,na.rm = TRUE)
 # combined mean ssd
Combined_mean_ssd = mean(combined$ssd,na.rm = TRUE)
# combined_SSRT
Combined_SSRT_adapt = SSRT_adapt(combined)

#6. Slider stuff ------------------
# Slider Value for RSDI on each image type
# Trial 1
NegDistress     = Emotion$NegDistress[!is.na(Emotion$NegDistress)]
NegUpset        = Emotion$NegUpset[!is.na(Emotion$NegUpset)]

# Trial 2
NeuDistress     = Emotion$NeuDistress[!is.na(Emotion$NeuDistress)]
NeuUpset        = Emotion$NeuUpset[!is.na(Emotion$NeuUpset)]

# Trial 3
PosDistress     = Emotion$PosDistress[!is.na(Emotion$PosDistress)]
PosUpset        = Emotion$PosUpset[!is.na(Emotion$PosUpset)]

# #Trauma 1
# Derealiz        = Emotion$Derealiz[!is.na(Emotion$Derealiz)] 
# Dissoc          = Emotion$Dissoc[!is.na(Emotion$Dissoc)] 
# Emot_Avoid      = Emotion$Emot_Avoid[!is.na(Emotion$Emot_Avoid)] 

#trauma 1
CogAvoi         = df$CogAvoi[!is.na(df$CogAvoi)]
Deperson        = df$Deperson[!is.na(df$Deperson)]
Derealiz        = df$Derealiz[!is.na(df$Derealiz)] 
Dissoc          = df$Dissoc[!is.na(df$Dissoc)] 
Trauma_Distress = df$Trauma_Distress[!is.na(df$Trauma_Distress)] 
EmotAvoi        = df$EmotAvoi[!is.na(df$EmotAvoi)] 
Fog             = df$Fog[!is.na(df$Fog)]
PhysAvoi        = df$PhysAvoi[!is.na(df$PhysAvoi)]
PhysRx          = df$PhysRx[!is.na(df$PhysRx)]
Reexp           = df$Reexp[!is.na(df$Reexp)]
Trauma_Upset    = df$Trauma_Upset[!is.na(df$Trauma_Upset)]
CogAvoi_2       = df$CogAvoi_2[!is.na(df$CogAvoi_2)]
Deperson_2      = df$Deperson_2[!is.na(df$Deperson_2)]
Derealiz_2      = df$Derealiz_2[!is.na(df$Derealiz_2)]
Dissoc_2        = df$Dissoc_2[!is.na(df$Dissoc_2)]
Trauma_Distress_2 = df$Trauma_Distress_2[!is.na(df$Trauma_Distress_2)]
EmotAvoi_2      = df$EmotAvoi_2[!is.na(df$EmotAvoi_2)]
Fog_2           = df$Fog_2[!is.na(df$Fog_2)]
PhysAvoi_2      = df$PhysAvoi_2[!is.na(df$PhysAvoi_2)]
PhysRx_2        = df$PhysRx_2[!is.na(df$PhysRx_2)]
Reexp_2         = df$Reexp_2[!is.na(df$Reexp_2)]
Trauma_Upset_2  = df$Trauma_Upset_2[!is.na(df$Trauma_Upset_2)]

## combine into one data frame (row)

output_data = data.frame(
    participant,
    B1_Mean_GoRT, B1_mean_ssd, B1_mean_SSRT, B1_SSRT_adapt, 
    B1_Go_ACC, B1_Stop_ACC, B1_mean_failed_RT, 
    B2_Mean_GoRT, B2_mean_ssd, B2_mean_SSRT, B2_SSRT_adapt, 
    B2_Go_ACC, B2_Stop_ACC, B2_mean_failed_RT,
    B3_Mean_GoRT, B3_mean_ssd, B3_mean_SSRT, B3_SSRT_adapt,
    B3_Go_ACC, B3_Stop_ACC, B3_mean_failed_RT,
    Combined_Mean_GoRT, Combined_mean_ssd, Combined_mean_SSRT, Combined_SSRT_adapt,     
    Combined_Go_ACC, Combined_Stop_ACC, Combined_mean_failed_RT,
    NegDistress, NegUpset, NeuDistress, NeuUpset, PosDistress, PosUpset,
    CogAvoi, Deperson, Derealiz, Dissoc, Trauma_Distress, EmotAvoi,
    Fog,  PhysAvoi, PhysRx, Reexp, Trauma_Upset,
    CogAvoi_2, Deperson_2, Derealiz_2, Dissoc_2, Trauma_Distress_2,
    EmotAvoi_2, Fog_2, PhysAvoi_2, PhysRx_2, Reexp_2,Trauma_Upset_2
)

df_output <- rbind(df_output,output_data)
view(df_output)

df_output
```

```{r}
REDCap_df<- read_csv("~/Downloads/TDCSAndInhibitoryCon_DATA_2025-01-31_0950.csv")

REDCap_par <- REDCap_df %>% 
  filter(stringr::str_detect(redcap_event_name, c("participant"))) %>% 
  dplyr::select(
    #demo info
    record_id,date,date_v2,demo_age:demo_medication_time,condition_v2,
    ## tdcs stuff
    tdcs_brainstim_v2,tdcs_seizure_v2,tdcs_conscious_v2,tdcs_stroke_v2,tdcs_tbi_v2,
    tdcs_illness_v2, tdcs_injury_v2, tdcs_headaches_v2, tdcs_headaches2_v2,
    tdcs_headmetal_v2,tdcs_medicaldevice_v2,tdcs_medications_v2,tdcs_medications2_v2,	
    tdcs_medications3_v2,stablemeds_v2,tdcs_pregnant_v2:tdcs_explain_v2,
    # TDSCS stuff?
    head___1:caffeine3,
    # Measures
    lec_a_1___1:lec_2_b_8_a,
    pcl5_1_sc:ptsd_checklist_score_sc,
    gad7_1:gad7_7,
    phq9_1:phq9_how_difficult,
    dss1:dss8,
    audit_yn:audit_q10,
    fnd1:fnd7,
    tbi1___1:tbi4___0, 
    ehq_1:ehq_4
  )

REDCap_clin <- REDCap_df %>% 
  filter(stringr::str_detect(redcap_event_name, c("clinicianadministe"))) %>% 
  select(
    record_id,
    cssrs1:cssrs05c,
    mini_clinician,psycheval,k23elig,mini_dx:mini_notes,
    condition:why,notes
  ) 

comp_REDCap_df <- left_join(REDCap_par, REDCap_clin, join_by(record_id== record_id)) 

SCR_df <- read_csv("~/Downloads/ParsedDataset_2025-01-27.csv") 

SCR_df <- SCR_df %>% 
  pivot_wider(
    names_from = Picture,
    values_from = c(HR,SCL)
        )

METRIC_data <- df_output %>% 
  mutate(
    XX_REDCap_DATA_XX = NA
  ) %>% 
  left_join(comp_REDCap_df, join_by(Subject == record_id)) %>% 
  mutate(
    XX_SCR_DATA_XX = NA
  ) %>% 
  left_join(SCR_df, join_by(Subject == Participant)) 

write_sav(METRIC_data,"~/Downloads/METRIC_FINAL.sav")
view(METRIC_data)

```


```{r}
library(ggtext)

METRIC_data %>% 
  ggplot() +
  geom_density(aes(x = B1_mean_ssd),fill= "#eb372a", alpha= .5, data = subset(METRIC_data, B1_mean_ssd > 0))+
  geom_density(aes(x = B1_Mean_GoRT),fill= "#1a60ed", alpha= .5)+
  geom_density(aes(x = B1_mean_SSRT), fill = "#2fbd42", alpha = .5) +
  theme_minimal()+
  labs(
    title = "Mean <span style='color:#eb372a'>SSD</span> and <span style='color:#1a60ed'>GoRT</span> and <span style='color:#2fbd42'>SSRT</span> during block 1.",
    subtitle = "Adding the max value to the GoRT worked. These values all look normalish!",
    x = "MS",
    y = "Density"
  ) +
  theme(
    plot.title = element_markdown(hjust = 0.5, size = 17),
    plot.subtitle = element_text(hjust = 0.5, size = 12)
  )
```


## KEY

Regarding restructuring the data into wide format and cleaning the data, this is what we need:

Participant number
Mean Block 1 GoRT
Block 1 Go Trials Correct
Block 1 Stop Trials correct
Block 1 SSRT
Mean Block 2 GoRT
Block 2 Go Trials Correct
Block 2 Stop Trials correct
Block 2 SSRT
Mean Block 3 GoRT
Block 3 Go Trials Correct
Block 3 Stop Trials correct
Block 3 SSRT
Combined Mean Block 2 + Block 3 GoRT
Combined Block 2 + Block 3 Go Trials Correct
Combined Block 2 + Block 3 Stop trials correct
Combined Block 2 + Block 3 SSRT
Slider Value for RSDI on each image type

Block Go vs Stop Trials
Block 1 = 150 Go, 50 Stop
Block 2 = 78 Go, 26 Stop
Block 2 = 78 Go, 26 Stop

## KEY
- Subject = Participant number
- Trial Type = BkGg (Black = Go trial, Red = Stop trial)
- GoAcc = Correct Go Response (1 = correct, 0 = incorrect)
- Go.RT = Go Reaction Time 
- GoDur = Stop Signal Delay (SSD)
- Inhs.ACC = Correct Stoppage (1 = correct, 0 = incorrect)
- Block = Running[Block] (Block 1, Block 2, Block 3)
- Slider Values for negative image = NegDistress.Slider1.Value, NegUpsetSlider1.Value
- Slider Values for neutral image = NeuDistress.Slider1.Value, NeuUpsetSlider1.Value
- Slider Values for positive image = PosDistress.Slider1.Value, PosUpsetSlider1.Value
- Slider Values for trauma images = every slider value that begins with "Trauma1" or "Trauma2". There should be 11 sliders for each trauma picture

